NFC and burnout in teachers - A replication and extension study

### 2021-08-31 Manuscript/Manuscript.Rmd
basic plot for the mediation model

#install.packages("here")       # easy file referencing
#install.packages("tidyverse")  # plotting and managing data
#install.packages("lavaan")     # for structural equation modelling
#install.packages("psych")      # Cronbach's Alpha and such
#install.packages("MVN")        # Mardia's test and such
#install.packages("MBESS")      # MacDonald's Omega
#install.packages("Hmisc")      # for correlations with p-values
#install.packages("kableExtra") # for great tables (see haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf)
#install.packages("knitr")      # for knitting documents and tables

library(here)
library(tidyverse)
library(ggplot2)
library(lavaan)
library(psych)
library(MVN)
library(MBESS)
library(Hmisc)
library(kableExtra)
library(knitr)
library(GGally)                 # from ggplot2, for multi-correlation plots

@@

>>>>

#install.packages("here")       # easy file referencing
#install.packages("tidyverse")  # plotting and managing data
#install.packages("lavaan")     # for structural equation modelling
#install.packages("psych")      # Cronbach's Alpha and such
#install.packages("MVN")        # Mardia's test and such
#install.packages("MBESS")      # MacDonald's Omega
#install.packages("Hmisc")      # for correlations with p-values
#install.packages("kableExtra") # for great tables (see haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf)
#install.packages("knitr")      # for knitting documents and tables
#install.packages("semPlot")    # plotting path models

library(here)
library(tidyverse)
library(ggplot2)
library(lavaan)
library(psych)
library(MVN)
library(MBESS)
library(Hmisc)
library(kableExtra)
library(knitr)
library(GGally)                 # from ggplot2, for multi-correlation plots
library(semPlot)

@@

```{r objective1_plot, echo=FALSE, message=FALSE, warning=FALSE}

  # Make a path diagram to visualize the results
  # (This is just okay, it is not the final version, e.g. there is no path from NCS to MBI yet)

  fit_plot <- semPaths(fit, what="par", # display the parameters on the arrows
                       layout = matrix(data = c(0,0,0,1,-1,0.5,0,-0.5,0,0), nrow = 5, ncol = 2), # manually set the node locations
                       sizeMan = 7, edge.label.cex = 0.8, # size specifications
                       fade = FALSE, # do not make insignificant associations invisible
                       theme = "colorblind" # select appropriate colour scheme
                       )
```
